MSOA Industrial Electricty and Gas maps

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Adding in cities in more detail

```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")
```
```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff/ndelec2010))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")##Why does this look like this? Increased efficiency? Businesses closing down?
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```

>>>>

```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")
```
```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff/ndelec2010))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")##Why does this look like this? Increased efficiency? Businesses closing down?
```
#####Cities in more detail
```{r Southampton MSOA difference in non dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```
